Geometry of Ranked Nearest Neighbour Interchange Space of Phylogenetic Trees

### 2019-12-01 rnni_convexity.tex
github link csort

The path $p$ returned by the algorithm $\csort$ is a shortest caterpillar path because every tree modification on $p$ reduces the number of inversions of taxa in $T$ and $R$.
\todo{Lena: If you decide to change the algorithm, mention here that what we've implemented is different from what is described here.}
\todo{Alex: I changed the algorithm. It shouldn't be too much work to change the implementation and the pseudo-code here. Do you want to keep the old version or shall I change everything to the new version?}
Note that any algorithm with this property returns a shortest caterpillar path.

>>>>

The path $p$ returned by the algorithm $\csort$ is a shortest caterpillar path because every tree modification on $p$ reduces the number of inversions of taxa in $T$ and $R$.
Our implementation of this algorithm can be found on GitHub \autocite{Collienne2019}.
